Statistical Detection of Collective Data Fraud

### 2019-12-09 Paper/ICME Template/TemplateVersion.tex
完成ICME模板文章

% Template for ICME 2020 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP/ICME LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,epsfig,amsfonts}
\usepackage{algorithm,algorithmicx,algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{rotating}
\usepackage{caption}
\usepackage{ulem}
\usepackage{multirow}
\usepackage{multicol}

@@

	\begin{abstract}
		Statistical divergence is widely applied in multimedia processing, basically due to regularity and explainable features displayed in data. However, in a broader range of data realm, these advantages may not out-stand, and therefore a more general approach is required. In data detection, statistical divergence can be used as an similarity measurement based on collective features.
		In this paper, we present a collective detection technique based on statistical divergence.
		The technique extracts distribution similarities among data collections, and then uses the statistical divergence to detect collective anomalies.
%		Our technique continuously evaluates metrics as evolving features and calculates adaptive threshold to meet the best mathematical expectation.
%		To illustrate details of the technique and explore its efficiency, we case-studied a real world problem of click farming detection against malicious online sellers. The evaluation shows that these techniques provided efficient classifiers. They were also sufficiently sensitive to a much smaller magnitude of data alteration, compared with real world malicious behaviours.
		Evaluation shows that it is applicable in the real world. 
	\end{abstract}

@@

		Data manipulation from outside hackers composes another potential threat of data frauds. \textit{Data Manipulation} here, according to a NSA definition, refers to behaviours which ``change information contained in those systems, rather than stealing data and holding it for ransom''.
		In 2013, hackers from Syria put up fake reports via Associated Press' Twitter account and caused a 150-point drop in the Dow~\cite{SyriaHacker}.

@@

		\subsection{Real World Problem: Click Farming Detection}\label{sec:related-realworld}
			Click farming is the behaviour that online sellers use a large number of customer accounts to create fake transaction records and give high remarks on products.
			There are two types of click farming behaviours: Centralized and Equalized.
			Equalized click farming refers to scenarios where behaviours are well organised while centralized does not.
			Current detection techniques for click farming mainly focus on user behaviours. Those techniques require platforms to keep records on user features. However, the detection can be easily bypassed by trained workers and some well programmed applications.

@@

	\section{Statistical Detection}\label{sec:algorithm-details}
		\subsection{Statistical Divergence Detection with Reference (SDD-R)}\label{sec:alg-opt-reference}
			Statistical divergence only provides a distance between two or more distributions. In a set of data collections, we can only draw a complete graph where nodes denote data collections and edges refer to the symmetric divergence between two connected nodes. From the graph we can find some points that have apparently larger distances with most of other points and return them as anomalies. This may work if anomalous nodes do not compose a large proportion. However the procedure will be too complicated to work out with large amounts of data. If it is assured that data collections form only one cluster, some optimizations can be applied to reduce complexity.

@@

			\begin{algorithm}[!t]
				\caption{SDD-R}
				\label{alg:sdd-r}
				\begin{algorithmic}[1]
					\Require Data Collections $\mathbb{D} = \{D_1, \dots, D_n\}$
					\Require Estimated anomalous probability $\alpha$
					\Ensure Anomalous Data Collections
					\For {$i \gets 1$ to $n$}
					\State $P_i \gets$ the distribution of $D_i$
					\EndFor
					\State $P_R \gets \frac{1}{n}\sum_{i = 1}^n P_i$
					\For {$i \gets 1$ to $n$}
					\State $d_i \gets D(P_i||P_R)$
					\EndFor
					\State $\mathcal{N}(\mu, \sigma) \gets$ Gaussian distribution estimated by $d_i$
					\State \Return $\{D_i | \frac{d_i - \mu}{\sigma} > 3 \}$
				\end{algorithmic}
			\end{algorithm}

@@

			By this approach, time complexity can be reduced from quadratic to linear. Fig.~\ref{fig:raw-overview} in Section~\ref{sec:exp-raw} demonstrates the result of the above process. Red distribution refer to the distances calculated from normal data collections, blue and green ones are from click-farmed data collections. Clearly, distances of normal data collections assembles together around a small value while anomalous ones lay around a larger distance value.

@@

			\begin{algorithm}[!t]
				\caption{SDD-E}
				\label{alg:sdd-e}
				\begin{algorithmic}[1]
					\Require Evidence set with normal data collections $\mathbb{E}_N = \{N_1, \dots, N_n\}$
					\Require Evidence set with anomalous data collections $\mathbb{E}_A = \{A_1, \dots, A_m\}$
					\Require Estimated anomalous probability $\alpha$
					\Require New data collection $\mathbb{D} = \{D_1, \dots, D_l\}$
					\Ensure Anomalous data collections in $\mathbb{D}$
					\For{$i \gets 1$ to $n$}
					\State $P_{N_i} \gets$ distribution of $D_{N_i}$\label{line:hist-1}
					\EndFor
					\For{$i \gets 1$ to $m$}
					\State $P_{A_i} \gets$ distribution of $D_{A_i}$\label{line:hist-2}
					\EndFor
					\State $P_R \gets \frac{1}{n}\sum_{i=1}^{n}P_{N_i}$
					\For{$i \gets 1$ to $n$}
					\State $d_{N_i} \gets D(P_{N_i}||P_R)$
					\EndFor
					\For{$i \gets 1$ to $m$}
					\State $d_{A_i} \gets D(P_{A_i}||P_R)$
					\EndFor
					\State $\mathcal{N}_N(\mu_N, \sigma_N) \gets$ normal distribution estimated from $\{d_{N_1}, \dots, d_{N_n}\}$
					\State $\mathcal{N}_A(\mu_A, \sigma_A) \gets$  normal distribution estimated from $\{d_{A_1}, \dots, d_{A_m}\}$
					\State $T \gets$ proper threshold derived from $\mathcal{N}_N$, $\mathcal{N}_A$ and $\alpha$
					\For{$i \gets 1$ to $l$}
					\State $P_i \gets$ distribution of $D_i$
					\State $d_i \gets D(P_i||P_R)$
					\EndFor
					\State \Return $\{D_i|d_i > T\}$
				\end{algorithmic}
			\end{algorithm}

@@

		\subsection{Threshold}\label{sec:alg-threshold}
			One important factor in algorithm SDD-E is the value of threshold.
%			A lower threshold rejects more instances, improving the sensitivity of anomalous data while increasing the number of false alarms. A higher threshold provide higher true negative rates yet neglecting more possible threats.
			A naive but prevalent approach is to set a fixed value as the threshold(As is shown in Algorithm~\ref{alg:sdd-r}).
%			This approach is easy to implement and may give satisfying results in specific cases.
			However, a fixed threshold requires specific analysis in the certain scenario, manual observations and tuning of parameters, which involves lots of human labour.
%			The rule of ``$3 \sigma$'' declares all instances outside $[\mu - 3\sigma, \mu + 3\sigma]$ to be anomalous. It can be used to automatically determine a threshold. But as a rigid metric, it is merely an estimation of a suitable boundary considering average situations, which is far from optimality when concrete data is provided. It would be either lower than the optimum if anomalous data lies far away from the normal cluster, or higher than the optimum if the anomalies sit close to the cluster centre.

			Fortunately, applying divergence as the distance measurement among data collections provides a fine property. With a reference distribution, divergences of normal data collections form a quasi-Gaussian distribution. The same applies to those anomalous ones.

			\begin{figure}[!t]
				\centering
				\includegraphics[width=\linewidth]{fig/ExampleThreshold.png}
				\caption{Optimal threshold should minimize the size of shadow under curve.}
				\label{fig:example-threshold}
			\end{figure}

			Moreover, as is verified in experiments, the meta-distribution of anomalous data collections lies in the right-hand-side to the normal one on the real line. As shown in Fig~\ref{fig:example-threshold}, the black curve displays the probability density function (PDF) fitting those divergences calculated from normal data collections; the blue curve displays the PDF derived from anomalous data collections. Threshold is chosen to minimize total errors(both false negative and false positive).

			Then the optimal threshold $T$ is calculated by minimizing total errors.
			However, this is not accurate enough, it implicates an assumption that chances are the same for a new data collection to be either anomalous or not. If we can determine the probability for a new data collection to be anomalous in any segment of data sequence, the equation should be modified as minimizing expected errors, where we use $\alpha$ to denote anomaly probability.

@@

	\section{Evaluation}\label{sec:evaluation}
		Our algorithm was implemented and interpreted in Python 3.5.2. All experiments were tested on Ubuntu 16.04. In the following experiments, we figured out properties of real world data and performance of our technique against anomalous data collections. We also made a comparison among variations of SDD algorithms and MGoF.\footnote{All resources and more detailed experiment results can be retrieved online: https://github.com/TramsWang/StatisticalAnomalyDetection}

@@

			The result showed that our technique outperformed MGoF in every real world case.
			SDD-E provided best performance, yet it consumed the most computing power. Comparison among SDD-R revealed improvement of reference as well as the importance of threshold under this technique. It is also clear that dynamic SDD-E is capable of tracing the gradual shift of environment. MGoF turned out to be the worst since it always mark several false positive when $c_{th}$ had not been met and much more false negatives when similar errors occurred too many.

@@

			From Fig.~\ref{fig:anomaly-magnitude} we can conclude that our algorithms are still the best, given that they are most sensitive toward tiny anomalous variations. However, static SDD-E did not rise until $\nu > 1$, this is because it suffered from fluctuation on the trade environment at the mean time. MGoF is not sensitive toward minor anomalies either.
			For a relatively small magnitude of click farming, the classifiers of MGoF quickly degrade to be trivial. The rigid threshold could not automatically rise up and was thus far from to optimal.

>>>>

% Template for ICME 2020 paper; to be used with:
%          spconf.sty  - ICASSP/ICIP/ICME LaTeX style file, and
%          IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,epsfig,amsfonts}
\usepackage{algorithm,algorithmicx,algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{rotating}
\usepackage{caption}
\usepackage{ulem}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{cuted}

@@

	\begin{abstract}
		Statistical divergence is widely applied in multimedia processing, basically due to regularity and interpretable features displayed in data. However, in a broader range of data realm, these advantages may not out-stand, and therefore a more general approach is required. In data detection, statistical divergence can be used as a similarity measurement based on collective features.
		In this paper, we present a collective detection technique based on statistical divergence.
		The technique extracts distribution similarities among data collections, and then uses the statistical divergence to detect collective anomalies.
%		Our technique continuously evaluates metrics as evolving features and calculates adaptive threshold to meet the best mathematical expectation.
%		To illustrate details of the technique and explore its efficiency, we case-studied a real world problem of click farming detection against malicious online sellers. The evaluation shows that these techniques provided efficient classifiers. They were also sufficiently sensitive to a much smaller magnitude of data alteration, compared with real world malicious behaviours.
		Evaluation shows that it is applicable in the real world. 
	\end{abstract}

@@

		General data frauds can be caused by manipulation from outside hackers.
%		Data manipulation from outside hackers composes another potential threat of data frauds.
		\textit{Data Manipulation} here, according to a NSA definition, refers to behaviours which ``change information contained in those systems, rather than stealing data and holding it for ransom''.
		In 2013, hackers from Syria put up fake reports via Associated Press' Twitter account and caused a 150-point drop in the Dow~\cite{SyriaHacker}.

@@

		\subsection{Real World Problem: Click Farming Detection}\label{sec:related-realworld}
			Click farming is the behaviour that online sellers use a large number of customer accounts to create fake transaction records and give high remarks on products.
			There are two types of click farming behaviours: centralized and equalized.
			Equalized click farming refers to scenarios where behaviours are well organised while centralized one does not.
			Current detection techniques for click farming mainly focus on user behaviours. Those techniques require platforms to keep records on user features. However, the detection can be easily bypassed by trained workers and some well programmed applications.

@@

	\section{Statistical Detection}\label{sec:algorithm-details}
		\subsection{Statistical Divergence Detection with Reference (SDD-R)}\label{sec:alg-opt-reference}
			Distortion or drift of certain distribution can be quantified by statistical divergence.
			It provides a distance between two or more distributions. In a set of data collections, we can only draw a complete graph where nodes denote data collections and edges refer to the symmetric divergence between two compared nodes. From the graph we can find some points that have apparently larger distances with most of other points and return them as anomalies. This may work if anomalous nodes do not compose a large proportion. However the procedure will be too complicated to work out with large amounts of data. If it is assured that data collections form only one cluster, some optimizations can be applied to reduce complexity.

@@

			\begin{algorithm}[!t]
				\caption{SDD-R}
				\label{alg:sdd-r}
				\begin{algorithmic}[1]
					\Require Data Collections $\mathbb{D} = \{D_1, \dots, D_n\}$
					\Require Divergence metric $div$
%					\Require Estimated anomalous probability $\alpha$
					\Ensure Anomalous Data Collections
					\For {$i \gets 1$ to $n$}
					\State $P_i \gets$ the distribution of $D_i$
					\EndFor
					\State $P_R \gets \frac{1}{n}\sum_{i = 1}^n P_i$
					\For {$i \gets 1$ to $n$}
					\State $d_i \gets div(P_i||P_R)$
					\EndFor
					\State $\mathcal{N}(\mu, \sigma) \gets$ Gaussian distribution estimated by $d_i$
					\State \Return $\{D_i | \frac{d_i - \mu}{\sigma} > 3 \}$
				\end{algorithmic}
			\end{algorithm}

@@

			By this approach, time complexity can be reduced from quadratic to linear. Fig.~\ref{fig:raw-overview} in Section~\ref{sec:exp-raw} demonstrates the result of the above process. Solid line refer to the distances calculated from normal data collections, dashed and dash-dotted ones are from click-farmed data collections. Clearly, distances of normal data collections assembles together around a small value while anomalous ones lay around a larger distance value.

@@

			\begin{algorithm}[!t]
				\caption{SDD-E}
				\label{alg:sdd-e}
				\begin{algorithmic}[1]
					\Require Evidence set with normal data collections $\mathbb{E}_N = \{N_1, \dots, N_n\}$
					\Require Evidence set with anomalous data collections $\mathbb{E}_A = \{A_1, \dots, A_m\}$
					\Require Divergence metric $div$
					\Require Estimated anomalous probability $\alpha$
					\Require New data collection $\mathbb{D} = \{D_1, \dots, D_l\}$
					\Ensure Anomalous data collections in $\mathbb{D}$
					\For{each $N_i\in \mathbb{E}_N, A_j\in \mathbb{E}_A, D_k\in \mathbb{D}$}
						\State $P_{N_i} \gets$ distribution of $N_i$\label{line:hist-1}
						\State $P_{A_j} \gets$ distribution of $A_j$\label{line:hist-2}
						\State $P_k \gets$ distribution of $D_k$
					\EndFor

%					\For{$i \gets 1$ to $n$}
%					\State $P_{N_i} \gets$ distribution of $N_i$\label{line:hist-1}
%					\EndFor
%					\For{$i \gets 1$ to $m$}
%					\State $P_{A_i} \gets$ distribution of $A_i$\label{line:hist-2}
%					\EndFor
					\State $P_R \gets \frac{1}{n}\sum_{i=1}^{n}P_{N_i}$
					\For{each $N_i\in \mathbb{E}_N, A_j\in \mathbb{E}_A$}
						\State $d_{N_i} \gets div(P_{N_i}||P_R)$
						\State $d_{A_j} \gets div(P_{A_j}||P_R)$
					\EndFor
%					\For{$i \gets 1$ to $n$}
%					\State $d_{N_i} \gets div(P_{N_i}||P_R)$
%					\EndFor
%					\For{$i \gets 1$ to $m$}
%					\State $d_{A_i} \gets div(P_{A_i}||P_R)$
%					\EndFor
					\State $\mathcal{N}_N(\mu_N, \sigma_N) \gets$ normal distribution estimated from $\{d_{N_1}, \dots, d_{N_n}\}$
					\State $\mathcal{N}_A(\mu_A, \sigma_A) \gets$  normal distribution estimated from $\{d_{A_1}, \dots, d_{A_m}\}$
					\State $T \gets$ proper threshold derived from $\mathcal{N}_N$, $\mathcal{N}_A$ and $\alpha$
%					\For{$i \gets 1$ to $l$}
%					\State $P_i \gets$ distribution of $D_i$
%					\State $d_i \gets div(P_i||P_R)$
%					\EndFor
%					\State \Return $\{D_i|d_i > T\}$
					\State \Return $\{D_i | div(P_i||P_R) > T\}$
				\end{algorithmic}
			\end{algorithm}

@@

		\subsection{Threshold}\label{sec:alg-threshold}
			\begin{figure}[t]
				\centering
				\includegraphics[width=\linewidth]{fig/ExampleThreshold.png}
				\caption{Optimal threshold should minimize the size of shadow under curve.}
				\label{fig:example-threshold}
			\end{figure}

			One important factor in algorithm SDD-E is the value of threshold.
%			A lower threshold rejects more instances, improving the sensitivity of anomalous data while increasing the number of false alarms. A higher threshold provide higher true negative rates yet neglecting more possible threats.
			A naive but prevalent approach is to set a fixed value as the threshold(As is shown in Algorithm~\ref{alg:sdd-r}).
%			This approach is easy to implement and may give satisfying results in specific cases.
			However, a fixed threshold requires specific analysis in the certain scenario, manual observations and tuning of parameters, which involves lots of human labour.
%			The rule of ``$3 \sigma$'' declares all instances outside $[\mu - 3\sigma, \mu + 3\sigma]$ to be anomalous. It can be used to automatically determine a threshold. But as a rigid metric, it is merely an estimation of a suitable boundary considering average situations, which is far from optimality when concrete data is provided. It would be either lower than the optimum if anomalous data lies far away from the normal cluster, or higher than the optimum if the anomalies sit close to the cluster centre.

%			Fortunately, applying divergence as the distance measurement among data collections provides a fine property. With a reference distribution, divergences of normal data collections form a quasi-Gaussian distribution. The same applies to those anomalous ones.

%			Moreover, as is verified in experiments, the meta-distribution of anomalous data collections lies in the right-hand-side to the normal one on the real line. As shown in Fig~\ref{fig:example-threshold}, the black curve displays the probability density function (PDF) fitting those divergences calculated from normal data collections; the blue curve displays the PDF derived from anomalous data collections.
			Threshold is chosen to minimize total errors(both false negative and false positive).
%			Then the optimal threshold $T$ is calculated by minimizing total errors.
			However, this is not accurate enough, it implicates an assumption that chances are the same for a new data collection to be either anomalous or not. If we can determine the probability for a new data collection to be anomalous in any segment of data sequence, the equation should be modified as minimizing expected errors, where we use $\alpha$ to denote anomaly probability.
			Suppose: $PDF_normal(x) \sim \mathcal{N}(\mu_n, \sigma_n)$ and $PDF_anomalous(x) \sim \mathcal{N}(\mu_a, \sigma_a)$, then adaptive threshold can be calculated by E.q.(\ref{equ:linear-weight}).

@@

			\begin{table*}
				\footnotesize
				\begin{align}\label{equ:linear-weight}
				T & = \mathop{\arg\min}_{T} \alpha\int_{0}^{T}PDF_{a}(x)dx +
				(1-\alpha)\int_{T}^{\sup(D)}PDF_{n}(x)dx\nonumber\\
				& \approx \mathop{\arg\min}_{T}
				\alpha\int_{-\infty}^{T}
				\frac{e^{-\frac{(x - \mu_a)^2}{2\sigma_a^2}}}{\sqrt{2\pi} \sigma_a}dx
				+ 
				(1-\alpha)\int_{T}^{+\infty}
				\frac{e^{-\frac{(x - \mu_n)^2}{2\sigma_n^2}}}{\sqrt{2\pi} \sigma_n}dx\nonumber\\
				& = \begin{cases}
				\displaystyle
				\frac{1}{\sigma_a^2 - \sigma_n^2}\left[(\sigma_a^2\mu_n - \sigma_n^2\mu_a) \pm \sigma_a\sigma_n\sqrt{(\mu_a - \mu_n)^2 + 2(\sigma_a^2 - \sigma_n^2)ln\frac{(1 - \alpha)\sigma_a}{\alpha\sigma_n}}\right], & \sigma_a \ne \sigma_n\\
				\displaystyle
				\frac{\mu_n + \mu_a}{2} + \frac{k^2ln\frac{1 - \alpha}{\alpha}}{\mu_a - \mu_n}, & \sigma_a = \sigma_n = k
				\end{cases}
				\end{align}

				Note: when $\sigma_a \ne \sigma_n$, keep the root s.t. $\displaystyle \frac{\alpha (T - \mu_a)}{\sigma_a^3}e^{-\frac{(T - \mu_a)^2}{2\sigma_a^2}} < \frac{(1 - \alpha) (T - \mu_n)}{\sigma_n^3}e^{-\frac{(T - \mu_n)^2}{2\sigma_n^2}}$
			\end{table*}

	\section{Evaluation}\label{sec:evaluation}
		Our algorithm was implemented and interpreted in Python 3.5.2. All experiments were tested on Ubuntu 16.04. In the following experiments, we figured out properties of real world data and performance of our technique against anomalous data collections. We also made a comparison among variations of SDD algorithms and MGoF.
%		\footnote{All resources and more detailed experiment results can be retrieved online: https://github.com/TramsWang/StatisticalAnomalyDetection}
		\footnote{All resources and more detailed experiment results can be viewed in supplemental material.}

@@

			The result showed that our technique outperformed MGoF in every real world case.
			SDD-E provided best performance, yet it consumed the most computing power. Comparison between SDD-R and MGoF revealed improvement of reference as well as the importance of threshold under this technique. It is also clear that dynamic SDD-E is capable of tracing the gradual shift of environment. MGoF turned out to be the worst since it always mark several false positive when $c_{th}$ had not been met and much more false negatives when similar errors occurred too many.

@@

			From Fig.~\ref{fig:anomaly-magnitude} we can conclude that our algorithms are still the best, given that they are most sensitive toward tiny anomalous variations. However, static SDD-E did not rise until $\nu > 1$, this is because it suffered from fluctuation on the trade environment at the mean time. MGoF is not sensitive toward minor anomalies either.
			For a relatively small magnitude of click farming, the classifiers of MGoF quickly degrade to be trivial. The rigid threshold could not automatically rise up and was thus far from optimal.
